Pollen competition

### 2018-02-25 publication/manuscript.Rmd
Plot of coefficient estimations

>>>>

```{r model-results, fig.height = 2.5, fig.cap = "Model coefficients"}
loadd(tidied_models)

tidied_models %>%
  filter(term != "(Intercept)", 
         var_trans == 'log') %>%
  group_by(pollen_category,scale, model, term) %>%
  summarise(estimate = first(estimate)) %>%
  ggplot(aes(x = estimate, 
             colour = pollen_category, 
             fill = pollen_category)) +
  geom_vline(xintercept = 0, linetype = 2, size = 0.25) +
  geom_freqpoly(geom = 'area',
               # alpha = 0.25,
               position = position_identity(),
               draw_quantiles = c(0.5, 0.95, 0.05), 
               trim = F, 
               scale = "count",
               bins = 15) +
  pub_theme() +
  facet_grid(scale ~ term, scales = "free_x") +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1")
```
